The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-05 article.tex
removed removed msgs
expanded on introduction

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this a state detection system is added that allows agents to detect subversive or malfunctioning agents in their environment. This system is implemented on the TurtleBot platform using the Robot Operating System, and performance is also evaluated in the Gazebo simulator.

@@

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. These three components are part of a larger chain of trust, one which will be further developed and implemented in future work, that verifies all other components in an agent are not compromised\footnote{In the full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify the static software, dynamic software, control system and communication of the agent.}.

Communication between two agents focuses on confidentiality and integrity which can both be accounted for through proper encryption and the data fields inside the encrypted message. A challenge-response system is implemented in this paper which changes, or churns, on every round trip time providing fresh keys for the AES-256 encrypted payload. A timestamp and source mac address ensures not only that the message comes from the individual claiming to be the originator in the raw packet, but also that timing attacks can be properly guarded against. Communications is not the only input which needs protection however, an adversary can distort the sensor data of an agent in order to lead it in a stray. Another agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established usage envelope, which in the case of this paper is a pre-computed map. Since there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

@@

REMOVED EXPANDED EKF/UKF DISCUSSION

@@

REMOVED LENGTHY COORDINATE FRAME DESCRIPTIONS FROM HERE

>>>>

Mobile robot security is a rapidly developing area of interest in robotics. As mobile robotic systems become more present, the need for secure and reliable state estimation systems continues to grow. The increasing coverage of wireless networks and density of network cyber-physical systems has lead to an opportunity for distributed systems coordinated between multiple agents. This paper proposes a distributed state estimation system using Kalman filters with secure ad-hoc channel communications between the agents. On top of this is a state detection system validation that allows agents to detect subversive or malfunctioning agents in their environment. The detection of such compromised agents can be used to create a trusted set within a group, providing a multi-node trust system. A TurtleBot running Robot Operating System (ROS) platform is used for implementation and performance is also evaluated in the Gazebo simulator.

@@

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. In a full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify various modules of an agent such as the static software, dynamic software, control system and communication of the agent.

Communication between two agents focuses on confidentiality and integrity which can both be accounted for through proper encryption and the data fields inside the encrypted message. A challenge-response system is implemented in this paper which changes, or churns, on every round trip time providing fresh keys for the encrypted payload. The consequence of this design is that every communication is uniquely encrypted, closing doors for leakage of information. Timestamp and source mac address fields inside the encrypted payload ensures not only that the message comes from the individual claiming to be the originator in the raw packet, but also that timing attacks can be properly guarded against.

Once communication is secured, an adversary can distort the sensor data of an agent in order to lead it in a stray. An agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established usage envelope, a term coined here as a pre-computed state trajectory map. This map allows for a large variety of planning algorithms to be used. In light that there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

Redundant measurements in the system allow for an agents inside a trusted set to verify each other's locations. With and without feedback from others in the system, through the use of  several Kalman filters an agent is able to verify the positions of others relative to itself.

@@

@@
